Methods for Large Scale Learning to Rank

### 2014-09-08 report/Chapters/Implementation.tex
raw data file + visualisation R file

This chapter describes implementation details of the Learning-to-Rank algorithm parallel implementations in HDInsight that are either Hadoop, Microsoft Azure, or HDInsight and are not part of the algorithm specification itself. The first section of this chapter will briefly discuss the HDInsight platform, the Hadoop ecosystem components offered by HDInsight and, in this regard, the Hadoop components used for implementation of the algorithms described in Chapter \ref{chap:ltr_methods}.

>>>>

\label{chap:implementation}
This chapter describes implementation details of the Learning-to-Rank algorithm parallel implementations in HDInsight that are either Hadoop, Microsoft Azure, or HDInsight and are not part of the algorithm specification itself. The first section of this chapter will briefly discuss the HDInsight platform, the Hadoop ecosystem components offered by HDInsight and, in this regard, the Hadoop components used for implementation of the algorithms described in Chapter \ref{chap:ltr_methods}.
